Getting Started with the Graded Response Model (GRM): A gentle introduction and tutorial in R

### 2024-01-22 manuscript.qmd
manuscript submitted

# Transforming describe() output into a APA-formatted table
rwa <- subset(ds, select = Q1:Q22)
table1 <- psych::describe(rwa); table1 <- as.data.frame(table1)
table1 <- table1 %>% 
  rownames_to_column(var="Item") %>% 
  select(Item, mean, sd, min, max, range, n) %>% 
  rename(Mean=mean, SD=sd, Minimum=min, Maximum=max, Range=range) %>% 
  flextable() %>%
  theme_apa() %>% 
  line_spacing(part = "all") %>% 
  padding(padding.top = 5, padding.bottom = 5)
table1 <- colformat_double(x=table1, j="Minimum", digits = 0)
table1 <- colformat_double(x=table1, j="Maximum", digits = 0)
table1 <- colformat_double(x=table1, j="Range", digits = 0)
table1 <- colformat_double(x=table1, j="n", digits = 0)
table1
```

@@

rwa <- rwa %>%
  mutate_all(~na_if(., 0)) %>%  # Replacing 0 with NA in all columns.
  drop_na()  # Removing cases with any NA values.
unfav <- c("Q4","Q6","Q8","Q9","Q11","Q13","Q15","Q18","Q20","Q21") # Now we create a vector defining which items will be coded reversely.
rwa <- rwa %>% 
  mutate(across(all_of(unfav), ~ 10 - .))# We simply subtract the scores from 9 (the maximum) to reverse code the unfavorable items.
# Transforming describe() output into a APA-formatted table
table2 <- psych::describe(rwa); table2 <- as.data.frame(table2)
table2 <- table2 %>% 
  rownames_to_column(var="Item") %>% 
  select(Item, mean, sd, min, max, range, n) %>% 
  rename(Mean=mean, SD=sd, Minimum=min, Maximum=max, Range=range) %>% 
  flextable() %>% 
  theme_apa() %>% 
  line_spacing(part = "all") %>% 
  padding(padding.top = 5, padding.bottom = 5)
table2 <- colformat_double(x=table2, j="Minimum", digits = 0)
table2 <- colformat_double(x=table2, j="Maximum", digits = 0)
table2 <- colformat_double(x=table2, j="Range", digits = 0)
table2 <- colformat_double(x=table2, j="n", digits = 0)
table2
```

@@

table3 <- as.data.frame(coefs$items)
load <- as.data.frame(sum$rotF)
h2 <- as.data.frame(sum$h2)
table3 <- cbind(table3, load, h2)
table3 <- table3 %>% 
  rownames_to_column(var="Item") %>% 
  select(Item, a, b1, b2, b3, b4, b5, b6, b7, b8, rwa, h2) %>% 
  rename(λ=rwa) %>% 
  flextable() %>% 
  theme_apa() %>% 
  line_spacing(part = "all") %>% 
  padding(padding.top = 5, padding.bottom = 5)
table3 <- colformat_double(x=table3, j="a", digits = 2)
table3 <- colformat_double(x=table3, j="b1", digits = 2)
table3 <- colformat_double(x=table3, j="b2", digits = 2)
table3 <- colformat_double(x=table3, j="b3", digits = 2)
table3 <- colformat_double(x=table3, j="b4", digits = 2)
table3 <- colformat_double(x=table3, j="b5", digits = 2)
table3 <- colformat_double(x=table3, j="b6", digits = 2)
table3 <- colformat_double(x=table3, j="b7", digits = 2)
table3 <- colformat_double(x=table3, j="b8", digits = 2)
table3

@@

According to our analysis, the model overall does not fit the data well (*M*~2~(`r df`) = `r m2_stat`, *p* \< .005, *RMSEA* = `r rmsea`, *SRMSR* = `r srmsr`, TLI = `r tli`, CFI = `r cfi`), because there is a significant discrepancy between response patterns predicted by the model with the data, as shown by significant *M*~2~ statistics. All GOF statistics, except for CFI, do not indicate a good fit. Model misfit, in this case, may be caused by local dependency between the items. We will explore this issue further in the next part.

@@

table4 <- as.data.frame(item.fit)
table4 <- table4 %>%
  select(item, S_X2, df.S_X2, RMSEA.S_X2, p.S_X2) %>% 
  rename(Item=item, χ2=S_X2, df=df.S_X2, RMSEA=RMSEA.S_X2, p=p.S_X2) %>% 
  flextable() %>% 
  theme_apa() %>% 
  line_spacing(part = "all") %>% 
  padding(padding.top = 5, padding.bottom = 5)
table4 <- colformat_double(x=table4, j="χ2", digits = 2)
table4 <- colformat_double(x=table4, j="df", digits = 2)
table4 <- colformat_double(x=table4, j="RMSEA", digits = 2)
table4 <- colformat_double(x=table4, j="p", digits = 2)
table4

>>>>

# Transforming describe() output into a APA-formatted table
rwa <- subset(ds, select = Q1:Q22)
table2 <- psych::describe(rwa); table2 <- as.data.frame(table2)
table2 <- table2 %>% 
  rownames_to_column(var="Item") %>% 
  select(Item, mean, sd, min, max, range, n) %>% 
  rename(Mean=mean, SD=sd, Minimum=min, Maximum=max, Range=range) %>% 
  flextable() %>%
  theme_apa() %>% 
  line_spacing(part = "all") %>% 
  padding(padding.top = 5, padding.bottom = 5)
table2 <- colformat_double(x=table2, j="Minimum", digits = 0)
table2 <- colformat_double(x=table2, j="Maximum", digits = 0)
table2 <- colformat_double(x=table2, j="Range", digits = 0)
table2 <- colformat_double(x=table2, j="n", digits = 0)
table2
```

@@

rwa <- rwa %>%
  mutate_all(~na_if(., 0)) %>%  # Replacing 0 with NA in all columns.
  drop_na()  # Removing cases with any NA values.
unfav <- c("Q4","Q6","Q8","Q9","Q11","Q13","Q15","Q18","Q20","Q21") # Now we create a vector defining which items will be coded reversely.
rwa <- rwa %>% 
  mutate(across(all_of(unfav), ~ 10 - .))# We simply subtract the scores from 9 (the maximum) to reverse code the unfavorable items.
# Transforming describe() output into a APA-formatted table
table3 <- psych::describe(rwa); table3 <- as.data.frame(table3)
table3 <- table3 %>% 
  rownames_to_column(var="Item") %>% 
  select(Item, mean, sd, min, max, range, n) %>% 
  rename(Mean=mean, SD=sd, Minimum=min, Maximum=max, Range=range) %>% 
  flextable() %>% 
  theme_apa() %>% 
  line_spacing(part = "all") %>% 
  padding(padding.top = 5, padding.bottom = 5)
table3 <- colformat_double(x=table3, j="Minimum", digits = 0)
table3 <- colformat_double(x=table3, j="Maximum", digits = 0)
table3 <- colformat_double(x=table3, j="Range", digits = 0)
table3 <- colformat_double(x=table3, j="n", digits = 0)
table3
```

@@

table4 <- as.data.frame(coefs$items)
load <- as.data.frame(sum$rotF)
h2 <- as.data.frame(sum$h2)
table4 <- cbind(table4, load, h2)
table4 <- table4 %>% 
  rownames_to_column(var="Item") %>% 
  select(Item, a, b1, b2, b3, b4, b5, b6, b7, b8, rwa, h2) %>% 
  rename(λ=rwa) %>% 
  flextable() %>% 
  theme_apa() %>% 
  line_spacing(part = "all") %>% 
  padding(padding.top = 5, padding.bottom = 5)
table4 <- colformat_double(x=table4, j="a", digits = 2)
table4 <- colformat_double(x=table4, j="b1", digits = 2)
table4 <- colformat_double(x=table4, j="b2", digits = 2)
table4 <- colformat_double(x=table4, j="b3", digits = 2)
table4 <- colformat_double(x=table4, j="b4", digits = 2)
table4 <- colformat_double(x=table4, j="b5", digits = 2)
table4 <- colformat_double(x=table4, j="b6", digits = 2)
table4 <- colformat_double(x=table4, j="b7", digits = 2)
table4 <- colformat_double(x=table4, j="b8", digits = 2)
table4

@@

According to our analysis, the model overall does not fit the data well (*M*~2~(`r df`) = `r m2_stat`, *p* \< .05, *RMSEA* = `r rmsea`, *SRMSR* = `r srmsr`, TLI = `r tli`, CFI = `r cfi`), because there is a significant discrepancy between response patterns predicted by the model with the data, as shown by significant *M*~2~ statistics. All GOF statistics, except for CFI, do not indicate a good fit. Model misfit, in this case, may be caused by local dependency between the items. We will explore this issue further in the next part.

@@

table5 <- as.data.frame(itemfit(fit))
table5 <- table5 %>%
  select(item, S_X2, df.S_X2, RMSEA.S_X2, p.S_X2) %>% 
  rename(Item=item, Sχ2=S_X2, df=df.S_X2, RMSEA=RMSEA.S_X2, p=p.S_X2) %>% 
  flextable() %>% 
  theme_apa() %>% 
  line_spacing(part = "all") %>% 
  padding(padding.top = 5, padding.bottom = 5)
table5 <- colformat_double(x=table5, j="Sχ2", digits = 2)
table5 <- colformat_double(x=table5, j="df", digits = 0)
table5 <- colformat_double(x=table5, j="RMSEA", digits = 3)
table5 <- colformat_double(x=table5, j="p", digits = 3)
table5
